---
title: "spotify-viz"
author: "Archi Parekh"
date: "9/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("knitr")
library("formatR")
library(tidyverse)
library(spotifyr)
library(jsonlite)
library(lubridate)
```

## Goal

I want to find the mood of all of my playlists and how they have changed over time.

1) Get all user playlists
2) Get all tracks for each playlist
3) Somehow aggregate the mood of the song
4) Somehow quantify each playlist's mood
5) Find the time range of its creation. 
6) Plot it all. 
```{r}
creds <- read_json("creds.json") # read creds

Sys.setenv(SPOTIFY_CLIENT_ID = creds$id) # set creds
Sys.setenv(SPOTIFY_CLIENT_SECRET = creds$secret)

access_token <- get_spotify_access_token() # retrieve access token
username = 'someone1623'
```

```{r}
my.tracks <- get_my_top_artists_or_tracks(type = 'tracks', time_range = 'long_term', limit = 20)
View(my.tracks)
```

```{r}
track.audio.features <- get_track_audio_features(my.tracks$id)
View(track.audio.features)
```

```{r}
df <- as.data.frame(cbind(my.tracks$name, track.audio.features$energy))
colnames(df) <- c("Name", "Energy")
```

```{r}
p<-ggplot(data=df, aes(x=Name, y=Energy)) +
  geom_bar(stat="identity", fill="steelblue") + 
  coord_flip() +
  theme_minimal() +
  ggtitle("Energy of my top 20 songs of all time")
p
```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
